---
title: "Untitled"
author: "Tushar  Nahar"
date: "October 4, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

#################################################################################
## 
##	These questions are very similar to those in the book
##	except we use different data set
##	We will consider weekly returns of  6 stocks starting 2008-03-19,
##  	 Amazon, 3M, Boeing, Visa, UnitedHealth, Micron Technology
##
#################################################################################
##
##	Download Data, get weekly returns in "%" called y.dat 

```{r}
library(xts);
library(quantmod);

syb = c("AMZN", "MMM", "BA", "V", "UNH","MU");
y.dat = get(getSymbols(syb[1],from = "2008-03-19"))
y.dat = weeklyReturn(Ad(y.dat),type = "log")
for(i in 2:length(syb)){
	y= get(getSymbols(syb[i], from = "2008-03-19"))
	y.dat = cbind(y.dat, weeklyReturn(Ad(y), type = "log"))
}
y.dat = 100*y.dat # covert to %
colnames(y.dat) = syb; # assign column names
head(y.dat,2); tail(y.dat,2);

```
#################################################################################
##
##  Problem 1.
##	First consider the weights w without constraints, except
##	they sum up to 1.
##
##	a. Find the minimum variance portfolio: its expect return, its risk, weights
##	b. Find the tangency portfolio: its expect return, its risk, weights
##	c. Plot the efficient frontier, the tangency portfolio,
##		the minimum variance portfolio,  location of each stock.
##		The annual risk-free rate is 3%, convert it to weekly (52 weeks a  year).
##		Find and plot the efficient portfolios (combing with risk free asset),
##		This is the line connect risky free portfolio (0, mu.f) and tangency 
##		portfolio (sd.T, mu.T): lines(c(0,sd.T), c(mu.f, mu.T))
##	d. Find the efficient porfolio of an allowed risk 2%. Compute its return.  
##	e. Find the efficient portfolio of a target return 0.45%. Compute its risk.
##	f. Find the efficient portfolio of a target return 0.8%. Compute its risk. 
##	You will use solve.QP() which requires R's quadprog package.
##	Detail information is given in handout. R code examples are given in  
##			the Book and its website
##	Evaluate portfolios with returns mu.R = seq(0,1,0.001)
##	You will find it helpful to assign column names to the weight matrix
##	set xlim = c(0,8.1) and ylim = c(0,1) for the plot
##
#################################################################################'
(a)
```{r}
library(quadprog);
y.dat.mu = apply(y.dat,2,mean);y.dat.mu
y.dat.S2 = var(y.dat); y.dat.S2
N =6;Amat = cbind(rep(1,N))
bvec = c(1)
out = solve.QP(Dmat = y.dat.S2, dvec = rep(0,N), Amat = Amat, bvec = bvec, meq =1)
cat("weights of the portfolio:\n", out$solution,"\n")
cat("Risk of the portforio is\n", sqrt(2*out$value),"\n")
y.dat.expectedreturn=t(y.dat.mu)%*%as.vector(out$solution)
cat("expected return of the portforio is\n", y.dat.expectedreturn,"\n")

```
(b)
```{r}
mu.R = seq(0, 1, 0.001);
sd.R = c(); wmat = matrix(nrow = length(mu.R), ncol = N);Amat = cbind(y.dat.mu, rep(1,N))
for(i in 1:length(mu.R)){
result = solve.QP(Dmat = y.dat.S2, dvec = rep(0,N), Amat=Amat,
bvec = c(mu.R[i],1), meq = 2);
sd.R[i] = sqrt(2*result$value)
wmat[i,] = result$solution
}

```

```{r}
mu.f = 3/52
sharpe = (mu.R - mu.f)/sd.R
i.T = which.max(sharpe)
cat("The tangency portfolio:\n expected return = ", mu.R[i.T], " risk =",
sd.R[i.T], "\n weights:\n"); round(wmat[i.T,],4)

```
(c)
```{r}
i.min=which.min(sd.R)
w_each=diag(rep(1,N))
sd_each=diag(y.dat.S2)
sd_each
m_each
m_each=y.dat.mu%*%w_each
plot(sd.R[mu.R>=mu.R[i.min]],mu.R[mu.R>=mu.R[i.min]],xlim = c(0,8.1),ylim = c(0,1),col="red")
lines(c(0,sd.R[i.T]), c(mu.f, mu.R[i.T]),col="blue")
sd.R[mu.R=round(m_each,digits = 3)]
mu.R[mu.R=round(m_each,digits  = 3)]
points(sd.R[mu.R==round(m_each,digits = 3)],mu.R[mu.R=round(m_each,digits == 3)])
```

