
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

#################################################################################
## 
##	These questions are very similar to those in the book
##	except we use different data set
##	We will consider weekly returns of  6 stocks starting 2008-03-19,
##  	 Amazon, 3M, Boeing, Visa, UnitedHealth, Micron Technology
##
#################################################################################
##
##	Download Data, get weekly returns in "%" called y.dat 
```{r}
library(xts);
library(quantmod);

syb = c("AMZN", "MMM", "BA", "V", "UNH","MU");
y.dat = get(getSymbols(syb[1],from = "2008-03-19"))
y.dat = weeklyReturn(Ad(y.dat),type = "log")
for(i in 2:length(syb)){
	y= get(getSymbols(syb[i], from = "2008-03-19"))
	y.dat = cbind(y.dat, weeklyReturn(Ad(y), type = "log"))
}
y.dat = 100*y.dat # covert to %
colnames(y.dat) = syb; # assign column names
head(y.dat,2); tail(y.dat,2);

```
#################################################################################
##
##  Problem 1.
##	First consider the weights w without constraints, except
##	they sum up to 1.
##
##	a. Find the minimum variance portfolio: its expect return, its risk, weights
##	b. Find the tangency portfolio: its expect return, its risk, weights
##	c. Plot the efficient frontier, the tangency portfolio,
##		the minimum variance portfolio,  location of each stock.
##		The annual risk-free rate is 3%, convert it to weekly (52 weeks a  year).
##		Find and plot the efficient portfolios (combing with risk free asset),
##		This is the line connect risky free portfolio (0, mu.f) and tangency 
##		portfolio (sd.T, mu.T): lines(c(0,sd.T), c(mu.f, mu.T))
##	d. Find the efficient porfolio of an allowed risk 2%. Compute its return.  
##	e. Find the efficient portfolio of a target return 0.45%. Compute its risk.
##	f. Find the efficient portfolio of a target return 0.8%. Compute its risk. 
##	You will use solve.QP() which requires R's quadprog package.
##	Detail information is given in handout. R code examples are given in  
##			the Book and its website
##	Evaluate portfolios with returns mu.R = seq(0,1,0.001)
##	You will find it helpful to assign column names to the weight matrix
##	set xlim = c(0,8.1) and ylim = c(0,1) for the plot
##
#################################################################################
(a)
```{r}
library(quadprog)
y.dat.mu = apply(y.dat,2,mean);y.dat.mu
y.dat.s2= var(y.dat)
N = 6;Amat = cbind(rep(1,N))
bvec = c(1)
out = solve.QP(Dmat = y.dat.s2, dvec = rep(0,N), Amat = Amat, bvec = bvec, meq =1)
cat("Return of the portforio is\n", t(y.dat.mu)%*%as.vector(out$solution),"\n")
cat("Risk of the portforio is\n", sqrt(2*out$value),"\n")
cat("weights of the portfolio:\n", out$solution)
```
(b)
```{r}
mu.R = seq(0, 1, 0.001);
sd.R = c(); wmat = matrix(nrow = length(mu.R), ncol = N)
Amat=cbind(y.dat.mu, rep(1,N))
for(i in 1:length(mu.R)){
result = solve.QP(Dmat = y.dat.s2, dvec = rep(0,N), Amat=Amat,
bvec = c(mu.R[i],1), meq = 2);
sd.R[i] = sqrt(2*result$value)
wmat[i,] = result$solution
}


mu.f = 3/52
sharpe = (mu.R - mu.f)/sd.R
i.T = which.max(sharpe)
cat("The tangency portfolio:\n expected return = ", mu.R[i.T], "\n risk =",
sd.R[i.T], "\n weights:\n"); round(wmat[i.T,],4)
```
(c)

```{r}
i.min = which.min(sd.R)
plot(sd.R[mu.R>=mu.R[i.min]],mu.R[mu.R>=mu.R[i.min]],col="red",xlim= c(0,8.1),ylim = c(0,1))
lines(c(0,sd.R[i.T]), c(mu.f, mu.R[i.T]),col="blue")
points(sd.R[i.T],mu.R[i.T],pch =19,col="blue")
points(sd.R[i.min],mu.R[i.min],pch =20 ,col = "yellow")
i.max =which.max(mu.R)
mu.R[i.max]
lines(sd.R,mu.R)
points(sqrt(diag(y.dat.s2)), round(y.dat.mu,digits = 3), pch=23 ,col="green")

```

(d)

```{r}
w_p = 2/sd.R[i.T] # risk allowed: sig_p = 1.8
cat("The maximum return of portfolio with risk 1 is:",
round((1-w_p)*mu.f + w_p*mu.R[i.T],4), "\n The weights are:\n");
round(c(risk_free = (1-w_p), w_p*wmat[i.T,]),4)
```

(e)

```{r}
w_p = (0.45-mu.f)/(mu.R[i.T]-mu.f) # target return: mu_p = 0.36%
cat("The efficient protfolio(lowest risk) with 0.45% return is:", round(w_p*sd.R[i.T],4),
"\n The weights are:\n");round(c(risk_free = (1-w_p), w_p*wmat[i.T,]),4)
```
(f)

```{r}
w_p = (0.8-mu.f)/(mu.R[i.T]-mu.f) # target return: mu_p = 0.36%
cat("The lowest risk with 0.36% return is:", round(w_p*sd.R[i.T],4),
"\n The weights are:\n");round(c(risk_free = (1-w_p), w_p*wmat[i.T,]),4)
```

#################################################################################
##
##	Problem 2.
##	Consider the portfolio with additional constraints -0.1 <= wi <= 0.4
##	a. First find the feasible set of expected returns using solveLP() in 
##		R's linprog package, report the lower and upper bounds, lb and ub
##
##	b. Repeat Problem 1 with constrained wi's using solve.QP and evaluating
##		returns mu.R between lb and ub. Use finer grid, say 0.0001 spacing.
##		You probably need to exclude the the two boundry points if they do not
##		yield feasible solution.
##		You may find page 128 of our handout helpful.
##		For the comparison purpose, use the same scale for the plot by setting
##		xlim = c(0,8.1) and ylim = c(0,1) and for the plot.
##		Not all the efficient portfolios you are asked to compute feasible. 
##		Identify them and explain why they are infeasible.
##	c. Comment on the difference between with and without constraints on wi's.
##		
#################################################################################

(a)
```{r}
library(linprog)
b1 = 0.4; b2 = 0.1
cvec = c(y.dat.mu, -y.dat.mu)
Amat.lp = rbind(diag(2*N), c(rep(1,N), rep(-1,N)))
bvec.lp = c(rep(b1,N), rep(b2,N),1)
inequ = c(rep("<=", 2*N), "=")
min.lp = solveLP(cvec = cvec, bvec = bvec.lp, Amat = Amat.lp,
lpSolve=T, const.dir = inequ, maximum = F)
max.lp = solveLP(cvec = cvec, bvec = bvec.lp, Amat = Amat.lp,
lpSolve=T, const.dir = inequ, maximum = T)
mu.lim = c(lower = min.lp$opt, upper = max.lp$opt);
lb=min.lp$opt
ub=max.lp$opt
```

(b)

```{r}
Amat = cbind(y.dat.mu, rep(1,N), -diag(rep(1,N)), diag(rep(1,N)))
mu.R = seq(round(lb,5),round(ub,5),0.0001);
sd.R = c(); wmat = matrix(nrow = length(mu.R), ncol = N)
for(i in 1:length(mu.R)){
result = solve.QP(Dmat = y.dat.s2, dvec = rep(0,N), Amat=Amat,
bvec = c(mu.R[i],1, rep(-b1, N), rep(-b2,N)), meq = 2);
sd.R[i] = sqrt(2*result$value)
wmat[i,] = result$solution
}
i.min = which.min(sd.R)
cat("The minimum variance portfolio:\n expected return = ", mu.R[i.min], " risk =",
sd.R[i.min], "\n weights:\n"); round(wmat[i.min,],4)

mu.f = 3/52
sharpe = (mu.R - mu.f)/sd.R
i.T = which.max(sharpe)
cat("The tangency portfolio:\n expected return = ", mu.R[i.T], "\n risk =",
sd.R[i.T], "\n weights:\n"); round(wmat[i.T,],4)


```

```{r}
plot(sd.R[mu.R>=mu.R[i.min]],mu.R[mu.R>=mu.R[i.min]],col="red",xlim= c(0,8.1),ylim = c(0,1))
lines(c(0,sd.R[i.T]), c(mu.f, mu.R[i.T]),col="blue")
points(sd.R[i.T],mu.R[i.T],pch =19,col="blue")
points(sd.R[i.min],mu.R[i.min],pch =20 ,col = "yellow")
points(sqrt(diag(y.dat.s2)), round(y.dat.mu,digits = 3), pch=23 ,col="green")
lines(sd.R,mu.R)
```
Both the tangency portolio and minimum variance which was computed beofre are not a part of the plot since they dont satisfy the box constraints
```{r}
i.max =which.max(mu.R)
mu.R[i.max]
```

(c) We can see that by adding the box constraints none of the portfolio has a weight of more than 0.4 and hence none of thes points are a part of the plot .
We can also see that there was much more higher weightage on the amazon stock in the tangential portfolio without box constraints than the one with box constraints
We can also see that the risk of the minimum variance porfolio(with box constraints -2.66) is higher than that off the one found in portfolio selected without the box constraints(-2.62)
Max return of the portfolio with the box constraints(0.52) is lesser than that of the one without the box constraints(1)

#############################################################################################################
##Rlab 16.10.2
##Problem 4
############################################################################################################

```{r}
setwd("C:/Users/tusha/Downloads")
dat = read.csv("FourStocks_Daily2013.csv", header = TRUE)
head(dat)
prices = dat[,-1]
n = dim(prices)[1]
returns = 100*(prices[-1,] / prices[-n,] - 1)
```


```{r}
y.returns.mu = apply(returns,2,mean);
y.returns.s2= var(returns)
N = 4
b1 = 0.5; b2 = 0.5


Amat = cbind(y.returns.mu, rep(1,N), -diag(rep(1,N)), diag(rep(1,N)))
mu.R = seq(round(0.045,5),round(0.06,5),0.0001);
sd.R = c(); wmat = matrix(nrow = length(mu.R), ncol = N)
for(i in 1:length(mu.R)){
result = solve.QP(Dmat = y.returns.s2, dvec = rep(0,N), Amat=Amat,
bvec = c(mu.R[i],1, rep(-b1, N), rep(-b2,N)), meq = 2);
sd.R[i] = sqrt(2*result$value)
wmat[i,] = result$solution
}
i.min = which.min(sd.R)

mu.f = 1.3/52
sharpe = (mu.R - mu.f)/sd.R
i.T = which.max(sharpe)
cat("The tangency portfolio:\n weights:\n"); round(wmat[i.T,],4)
cat("The sharpe's ratio for tangency portfolio is " ,sharpe[i.T] )
plot(sd.R[mu.R>=mu.R[i.min]],mu.R[mu.R>=mu.R[i.min]],col="red",xlim=c(0,1.3) ,ylim=c(0,0.060))
lines(c(0,sd.R[i.T]), c(mu.f, mu.R[i.T]),col="blue")
points(sqrt(diag(y.returns.s2)), round(y.returns.mu,digits = 3), pch=23 ,col="green")

```

