---
title: "Homework 6"
author: "Tushar  Nahar"
date: "October 10, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

1. Use the weekly returns of 6 stoacks data from the last homework. Please note that they are in %.

(a) Fit a multivariate-t distribution to the data.

(b) Suppose you are going to invest $20,000 on assets. Compute the t-parametric one-week VaR and ES at alpha = 0.05 of the minmum variance portfolio and tangency portfolio.

```{r}
library(xts);
library(quantmod);
syb = c("AMZN", "MMM", "BA", "V", "UNH","MU");
y.dat = get(getSymbols(syb[1],from = "2008-03-19"))
y.dat = weeklyReturn(Ad(y.dat),type = "log")
for(i in 2:length(syb)){
	y= get(getSymbols(syb[i], from = "2008-03-19"))
	y.dat = cbind(y.dat, weeklyReturn(Ad(y), type = "log"))
}
y.dat = 100*y.dat # covert to %
colnames(y.dat) = syb; # assign column names
head(y.dat,2); tail(y.dat,2);

```
(a)
```{r}
library(MASS); library(mnormt)
nu.seq = seq(4,7,0.001)
loglik = c()
for(i in 1:length(nu.seq)){
out = cov.trob(y.dat, nu = nu.seq[i])
loglik[i] = sum(dmt(y.dat,mean = out$center, S = out$cov, df = nu.seq[i], log = T))
}
nu = nu.seq[which.max(loglik)];fit = cov.trob(y.dat, nu = nu)
est = list(nu = nu, mean = fit$center, Lambda = fit$cov)
est
```
(b)
```{r}
library(quadprog)
N = 6;
mu.R = seq(0, 1, 0.001);
sd.R = c(); wmat = matrix(nrow = length(mu.R), ncol = N)
Amat=cbind(est$mean, rep(1,N))
for(i in 1:length(mu.R)){
result = solve.QP(Dmat = est$Lambda, dvec = rep(0,N), Amat=Amat,
bvec = c(mu.R[i],1), meq = 2);
sd.R[i] = sqrt(2*result$value)
wmat[i,] = result$solution
}
i.min = which.min(sd.R)
w.min=wmat[i.min,]
cat("Minimum variance portfolio:\n"); round(w.min,4)
mu.P = t(w.min%*%est$mean)/100;
lambda.P = sqrt(t(w.min)%*%est$Lambda%*%w.min)/100; nu = est$nu
cat("Parametric estimates of portfolio:\n",
paste(c("\t mu.P", "\t lambda.P", "\t nu"),
round(c(mu.P, lambda.P, nu),4), sep = " = "))
alpha = 0.05; S = 20000
q.t = qt(alpha, df = nu); VaR.P = -S*(mu.P + lambda.P*q.t);
ES.P = S*(-mu.P+lambda.P*dt(q.t,nu)/alpha*(nu+q.t^2)/(nu-1))
cat("\none-week risk estimates: ",paste(c("VaR","\t ES"),
round(c(VaR.P,ES.P),4), sep = " = "))
mu.f = 3/52
sharpe = (mu.R - mu.f)/sd.R
i.T = which.max(sharpe)
cat("\nThe tangency portfolio:\n expected return = ", mu.R[i.T], "\n risk =",
sd.R[i.T], "\n weights:\n"); round(wmat[i.T,],4)
w.T=wmat[i.T,]
mu.P = t(w.T%*%est$mean)/100;
lambda.P = sqrt(t(w.T)%*%est$Lambda%*%w.T)/100;
cat("Parametric estimates of portfolio:\n",
paste(c("\t mu.P", "\t lambda.P", "\t nu"),
round(c(mu.P, lambda.P, nu),4), sep = " = "))
alpha = 0.05; S = 20000
q.t = qt(alpha, df = nu); VaR.P = -S*(mu.P + lambda.P*q.t);
ES.P = S*(-mu.P+lambda.P*dt(q.t,nu)/alpha*(nu+q.t^2)/(nu-1))
cat("\none-week risk estimates: ",paste(c(" VaR"," ES"),
round(c(VaR.P,ES.P),4), sep = " = "))
```

2. Get the stock quotes of Nike Inc., the ticker symbol is "NKE". Please do not specifying dates, the default is from 2017-01-01 to the current date. Do problem 1 of Exercises 19.12 with the log daily returns of Nike. 
(a)
```{r}
getSymbols("NKE")
SPrt = dailyReturn(Ad(NKE), type = "log")[-1]
head(SPrt,1); tail(SPrt,1); cat("Sample size n = ", dim(SPrt)[1])
alpha = 0.01; q = quantile(SPrt, alpha);S = 1000;
VaR.np = -S*q; ES.np = -S*mean(SPrt[SPrt < q])
cat("\nNonparametric estimates:\n ", paste(c("0.01-quantile"," VaR"," ES"),
round(c(q, VaR.np,ES.np),4), sep = " = "))

```
(b)
```{r}
library(MASS)
alpha = 0.01; S = 1000;
fit.norm = fitdistr(SPrt, "normal");
fit.norm$est
mu = fit.norm$est["mean"];sigma = fit.norm$est["sd"]
q.norm = qnorm(alpha, mean = mu ,sd=sigma); VaR.norm = -S*(mu + sigma*q.norm)
ES.norm = S*(-mu+(sigma*dnorm(q.norm,mean =mu,sd= sigma)/alpha))
cat("Parametric t estimates:\n ",paste(c("0.01-quantile"," VaR"," ES"),
round(c(mu + sigma*q.norm, VaR.norm,ES.norm),4), sep = " = "))

```
(c)
```{r}
alpha = 0.01; S = 1000;
fit.t = fitdistr(SPrt, "t");
fit.t$est
mu = fit.t$est["m"];lambda = fit.t$est["s"];nu = fit.t$est["df"];
q.t = qt(alpha, df = nu); VaR.t = -S*(mu + lambda*q.t)
ES.t = S*(-mu+lambda*dt(q.t,nu)/alpha*(nu+q.t^2)/(nu-1))
cat("Parametric t estimates:\n ",paste(c("0.01-quantile"," VaR"," ES"),
round(c(mu + lambda*q.t, VaR.t,ES.t),4), sep = " = "))
```
(d)
Since the sample size is large and alpha is not too small the non parametric estimate would provide a good estimate for Var and expected shortfall

Estimates of the t distribution are close to the non parametric estimate , this is expected since heavy tailed t distribution models log returns better than the normal distribution .

As seen , normal distribution does not provide a reasonable estimate of var or Expected shortfall



3. Use the daily returns of Nike for this problem. Find the regression estimate of tail index and compute the semiparametric estimate of the 24-hour VaR and ES. Use bandwidths m = 50, 100, 200 and 300.

Superimposing the least squares line to a scatter plot of x and y.

plot(x,y)

abline(lsfit(x,y)$coef)
```{r}
library(stats)
y.dailyreturns=dailyReturn(Ad(NKE))
n=length(y.dailyreturns)
yt = sort(as.numeric(y.dailyreturns)) # sort from smallest to largest
m = c(50,100,200,300); out = matrix(nrow = 3, ncol = 4)
dimnames(out)[[1]] = c("corr", "slope","ahat")
dimnames(out)[[2]] = paste("m", m, sep = " = ")
for(i in 1:4){
x = log((1:m[i])/n); y = log(-yt[1:m[i]])
out[1,i] = cor(x,y)
out[2,i] = lsfit(x,y)$coef[2] ## ols estimate of slope
plot(x,y,main =paste("m=",m[i]))

abline(lsfit(x,y)$coef)
}
out[3,] = -1/out[2,] ## ahat = -1/slope
out

a = out["ahat","m = 200"]
cat("\nRegression estimate for tail index:",a,"\n")
alpha0 = 0.1; alpha = seq(0.01,0.05,0.01)
VaR0 = -S*quantile(yt,alpha0)
cat("Nonparametric estimates: ", paste(c("0.1-quantile","\n VaR(.1)\n"),
round(c(quantile(yt,alpha0), VaR0), 4), sep = " = "))

VaR = VaR0*(alpha0/alpha)^(1/a); names(VaR) = paste(alpha)
ES = a/(a-1)*VaR
cat("\nSemiparametric Risk Estimate for alpha = ", alpha, ":\n");rbind(VaR,ES)


```
m=200 is chosen as the bandwith for calculation 24 hour estimates for Var and ES

4.Repeat Problem 3 with the Hill estimate for the tail index. 
```{r}
c = seq(quantile(y.dailyreturns,.01),quantile(y.dailyreturns,.25),by=.0005)
nc = c(); hill = c()
for (i in 1:length(c)){
nc[i] = sum(y.dailyreturns < c[i])
hill[i] = nc[i]/sum(log(y.dailyreturns[y.dailyreturns< c[i]]/c[i]))
}
plot(nc,hill)
## nc=150-200 shows an almost constant value and hence is chosen as the range to get the hill estimate
ind = which(nc > 150 & nc < 200); a.hill = mean(hill[ind])
cat("Hill estimates with nc in (150,200):\n", hill[ind],"\n average:", a.hill,"\n")
cat("\nThe estimate of tail index using hill estimate:",a.hill,"\n")
VaR = VaR0*(alpha0/alpha)^(1/a.hill); names(VaR) = paste(alpha)
ES = a.hill/(a.hill-1)*VaR
cat("Risk with Hill Estimate for alpha = ", alpha, ":\n");
rbind(VaR,ES)
```

