---
title: "Homework 1"
author: "Tushar  Nahar"
date: "September 4, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## R Markdown

Stock_FX_Bond.CSV contains daily and adjusted closing price of stocks and the S&P 500 and yields on bond from 2nd Jan 1987 to 1 Sep 2006.The following code loads the data , calculates from the CSV files and calculates the returns for General Motors and Ford 
```{r}
dat=read.csv("Stock_FX_Bond.csv", header = TRUE)
attach(dat)
n = dim(dat)[1]
GMReturn = GM_AC[-1] / GM_AC[-n] - 1
FReturn = F_AC[-1] / F_AC[-n] - 1
par(mfrow = c(1, 1))
plot(GMReturn,FReturn)
```
The scatterplots suggest that there us a positive correlation between  GM and Ford returns. Higer values of GM return occur with Higher values of Ford returns.There are a number of outlying points whose return values differ signifcantly from the mean values.Outlying GM return seem to occur with outlying ford returns.

In the following lines of code we calculate the log returns for GM and plot the returns versus the log returns.We then plot two types of returns.
```{r}
logGMReturn =log(GM_AC[-1] / GM_AC[-n])
par(mfrow = c(1, 1))
plot(GMReturn,logGMReturn)
print(cor(GMReturn,logGMReturn))
```
There GMReturn and logGMReturns has a pearsons correlation cofficient of more than 0.9995408(~1) which suggests that there is a very strong positive correlation between returns of GM  and log returns 

In the following lines of code we obtain the adjusted returns for Microsoft and Merck using the quantmod package and we plot these returns 
```{r}
library("quantmod")
getSymbols('MSFT',from = '2008-08-01',to ='2018-09-5')
getSymbols('MRK',from = '2008-08-01',to ='2018-09-5')
plot(cbind(Ad(MSFT),Ad(MRK)), legend.loc = "topleft")
MRK.daily=dailyReturn(MRK)
MSFT.daily=dailyReturn(MSFT)
plot(as.vector(MRK.daily),as.vector(MSFT.daily))
```
The scatter plot suggests that there is a positive correlation between daily returns of Microsoft and Merck. The higher than average returns of Merck occur with higher than average returns of Microsoft.There are returns which differ significantly from the average returns for both Microsoft and Merck and these returns occur together.

```{r}
MRK.daily.log=log(MRK.daily+1)
MSFT.daily.log=log(MSFT.daily+1)
plot(as.vector(MRK.daily),as.vector(MRK.daily.log))
print(cor(as.vector(MRK.daily),as.vector(MRK.daily.log)))
plot(as.vector(MSFT.daily),as.vector(MSFT.daily.log))
print(cor(as.vector(MSFT.daily),as.vector(MSFT.daily.log)))

```

The returns of both Merck and Microsoft have a very strong correlation with log rturns with the pearsons coeeficient value of ~1

We next consider a situation where a hedge fund has invested $50000 dollars and  has a leverage of 20:1. Assuming stock prices have a normal distribution with a yearly mean of 0.05 and a standard deviation of 0.23, We carry out a monte carlo simulation to obtain a sample probability that the minimum stock price would go below the borrowed amount.


```{r}
niter = 1e5 # number of iterations
below = rep(0, niter) # set up storage
set.seed(2009)
for (i in 1:niter)
{
r = rnorm(45, mean = 0.05/253,
sd = 0.23/sqrt(253)) # generate random numbers
logPrice = log(1e6) + cumsum(r)
minlogP = min(logPrice) # minimum price over next 45 days
below[i] = as.numeric(minlogP < log(950000))
 }
 mean(below)
```
The mean(below) function provides the propertion of values in simulation where the minimum prices is lesser than 950000 i,e the probability that the minimum price is lesser than 950000 is ~0.50988.

In the following section  we use simulation to see how stock prices evolve when the log returns  are iid normal, which implies that the price series is a geometric random walk.

There are 253 days in a year so the simulation is carried over one year


```{r}
 set.seed(2012)
 n = 253
par(mfrow=c(3,3))
for (i in (1:9))
{
logr = rnorm(n, 0.05 / 253, 0.2 / sqrt(253))
price = c(120, 120 * exp(cumsum(logr)))
plot(price, type = "b")
}
```

The price series in the given sample appear to have momentum in the short term .Increase in stock price is accompanied by an increase in stock price for a short run . This momentum does not continue over the long run . This appearance of momentum is an illusion since the rnorm function is designed to generate random number which are independent of each other and therefore have a correlation coefficient which is 0. Also from the first graph we can see that an initial increase price does not that there will be a continual increase in price. There is reversal in the direction of price change



In the following section we calculate the returns and logreturns  of McDonalds from 2010-01-01 to 2014-09-06
```{r}
getSymbols('MCD',from = '2010-01-01',to ='2014-09-06')
MCD.daily=dailyReturn(MCD)
MCD.daily.log=log(MCD.daily+1)
plot(as.vector(MCD.daily),as.vector(MCD.daily.log))
print(cor(as.vector(MCD.daily),as.vector(MCD.daily.log)))
print(head(MCD.daily))
print(as.vector(MCD.daily.log)[1:6])

```

The line is almost 45 degrees from both the axis and the axis have the same scale. Therefore the returns and log returns for MCD are approximately the same.This can also be seen from the printed values of returns and log returns

```{r}
mean(MCD.daily)
mean(MCD.daily.log)
sd(MCD.daily)
sd(MCD.daily.log)
```

The mean of daily retuns and log returns have a very small diffrence. The standard deviation have an even smaller diffrence and can be considered equal.It is reasonable to consider that the mean and standard deviation are the same log return and log normal retuns.


Paired t test is used to compare the means of return and log return 
```{r}
t.test(as.vector(MCD.daily),as.vector(MCD.daily.log),paired = TRUE)
```
p value of lesser than 0.05 is obtained.Therefore  we reject the current hypothesis that the mean diffrence between the paired diffrence is signifcantly diffrent from 0.

There are two assumption made while considering the paired t tests
-the diffrence of the means follow a normal distribution
-the diffrence are independent of each other


The diffrence of mean need not follow a normal distribution. The diffrence may not be independent of each other since the return values of may have correlation.The results of the t -test might not hold


Although the paired t-tests suggests that there is a significant diffrence between the mean. The tests migh not hold. Therfore it is reasonable to interchange the values between returns and log returns for very sm all values.

We next consider run a monte carlo simulation model assuming the distribution of MCD log returns is normal to estimate the risk that the minimum price of mcdonalds is below $85
considering the starting price is $93.07 dollars
```{r}
set.seed(2015)
n = 20
below=rep(0,10000)
for (i in (1:10000))
{
r = rnorm(n, mean(MCD.daily.log), sd(MCD.daily.log))
prices=93.07*exp(cumsum(r))
minP = min(prices) # minimum price over next 45 days
below[i] = as.numeric(minP < 85)
}
mean(below)

```
Computing yield to maturity

The following R function computes the price of a bond given coupon payments,maturity yield to maturity and par value

```{r}
bondvalue = function(c, T, r, par)
{
# Computes bv = bond values (current prices) corresponding
# to all values of yield to maturity in the
# input vector r
#
# INPUT
# c = coupon payment (semiannual)
# T = time to maturity (in years)
# r = vector of yields to maturity (semiannual rates)
# par = par value
#
bv = c / r + (par - c / r) * (1 + r)^(-2 * T)
bv
}
price = 1200 # current price of the bond
C = 40 # coupon payment
T= 30 # time to maturity
par = 1000 # par value of the bond
r = seq(0.02, 0.05, length = 300)
value = bondvalue(C, T, r, par)
yield2M = spline(value, r, xout = price) # spline interpolation
plot(r, value, xlab = "yield to maturity", ylab = "price of bond",
type = "l", main = "par = 1000, coupon payment = 40,T = 30", lwd = 2)
abline(h = 1200)
abline(v = yield2M)
```
The yield to maturity is ~0.325

```{r}
print(yield2M)
```
The estimate is approximately equal to the value obtained from spline interpolation.

Problem 2

The uniroot(function(r) r^2 - 0.5, c(0.7, 0.8)) finds the root of r^2 - 0.5 between 0.7 and 0.8

Problem 3
```{r}
bondvalue = function(c, T, r, par)
{
# Computes bv = bond values (current prices) corresponding
# to all values of yield to maturity in the
# input vector r
#
# INPUT
# c = coupon payment (semiannual)
# T = time to maturity (in years)
# r = vector of yields to maturity (semiannual rates)
# par = par value
#
bv = c / r + (par - c / r) * (1 + r)^(-2 * T)
bv
}
price = 1200 # current price of the bond
C = 40 # coupon payment
T= 30 # time to maturity
par = 1000 # par value of the bond
r = seq(0.02, 0.05, length = 300)
value = bondvalue(C, T, r, par)
yield2M=uniroot(function(r)bondvalue(C, T, r, par)-1200,c(0.02,0.05))
print(yield2M)

```
The yield2m for price of 1200 is  0.03238059

Problem 4
```{r}
price = 9800 # current price of the bond
C = 280 # coupon payment
T= 8 # time to maturity
par = 10000 # par value of the bond
value = bondvalue(C, T, r, par)
yield2M=uniroot(function(r)bondvalue(C, T, r, par)-9800,c(0.02,0.05))
print(yield2M)
r = seq(0.02, 0.05, length = 300)
plot(r, value, xlab = "yield to maturity", ylab = "price of bond",
type = "l", main = "par = 1000, coupon payment = 40,T = 30", lwd = 2)
abline(h = 9800)
abline(v = yield2M)
```
The yeild to maturity obtained is 0.02985708

Problem 5
```{r}
price = 1050 # current price of the bond
C = 35 # coupon payment
T= 20 # time to maturity
par = 1000 # par value of the bond
yield2M=uniroot(function(r)bondvalue(C, T, r, par)-1050,c(0.02,0.05))
print(yield2M)

```

The yeild to maturity obtained is 0.03275297


Problem 6
```{r}
price = 950.10 # current price of the bond
C = 35 # coupon payment
T= 5 # time to maturity
par = 1000 # par value of the bond
couppay=uniroot(function(c)bondvalue(c, T, 0.035, par)-950.10,c(0,2000))
print(couppay)

```

The coupon payment is 28.99996

3.11

Q13 0.8105

Q22
